Differences in care for patients experiencing left vs. right hemisphere ICH

### 2024-02-13 reports/aggressiveness.qmd
dag fixes

---
title: Differences in care for patients experiencing left vs. right hemisphere ICH
author: Nikhil Patel, MD
format: html
toc: true
---

```{r setup, output=FALSE, message=FALSE, warning=FALSE}
#| code-fold: false

library(targets)
library(readr)
library(tidyr)
library(skimr)
library(dplyr)
library(gt)
library(gtsummary)
library(ggplot2)
library(marginaleffects)
library(modelsummary)

theme_set(theme_minimal(base_family = "Figtree"))

tar_load(ich)
tar_load(non_surgery_trials)
tar_load(surgery_trials)
tar_load(table_1)
tar_load(table_2)

@@

>>>>

---
title: Differences in care for patients experiencing left vs. right hemisphere ICH
author: Nikhil Patel, MD
format:
  html: 
    mainfont: Figtree
    monofont: Source Code Pro
    fontsize: 0.97rem
    embed-resources: true
    toc: true
    toc-location: left
    toc-depth: 5
    toc-title: Contents
    smooth-scroll: true
    link-external-icon: true
    link-external-newwindow: true
    code-overflow: wrap
    code-tools: true
    highlight-style: nord
    lightbox: true
---

::: {.callout-note icon="false"}
## Research question

Do patients presenting with left hemispheric ICH receive less aggressive care (as measured by rates of neurosurgery, ventriculostomy, tracheostomy, PEG, and early withdrawal of life-sustaining therapies) as compared to those with right hemispheric ICH?

```{r setup, output=FALSE, message=FALSE, warning=FALSE}
#| code-fold: true
#| code-summary: "Loading Libraries and Other Code Setup"

library(targets)
library(skimr)
library(dplyr)
library(gt)
library(gtsummary)
library(ggplot2)
library(ggdag)
library(dagitty)
library(marginaleffects)
library(modelsummary)

# theme customization
theme_set(theme_minimal(base_family = "Figtree"))

theme_set(
  theme_dag() %+replace%
    # also add some additional styling
    theme(
      legend.position = "bottom",
      strip.text.x = element_text(margin = margin(2, 0, 2, 0, "mm"))
    )
)

# load all targets objects
tar_load_everything()

@@

```{r}
#| width: 1200
#| height: 2000
#| fig-align: center
#|

ggdag(aggressive_dag, use_labels = "label", text = FALSE)

ggdag_adjustment_set(aggressive_dag, shadow = TRUE, use_labels = "label", text = FALSE)

ggdag_adjustment_set(outcome_dag, shadow = TRUE, use_labels = "label", text = FALSE)

aggressive_dag |>
  ggdag_paths(shadow = TRUE, text = FALSE, use_labels = "label")

tidy_dagitty(aggressive_dag)
